An OpenCL Implementation of Wait-Free Sets

### 2015-07-07 Docs/paper.tex
doc changed

\begin{algorithm}
  \caption{finds a key and returns a window to it.}
  \label{alg:find}
  \begin{algorithmic}[1]
    \Require
        \Statex startRef:Reference to the starting node.
    \Ensure
       \Statex cleans all the logically deleted nodes.
    \Statex   
    \Function{find}{key, prevRef\&, nextRef\&, index\&}
      \State startRef = hash(key);
      \State prevRef = nextRef = {\it Null};
      \State index = 0;      
      \While(true)
        \State pRef = {\it Null};
        \State nRef = startRef;
        \State status = {\it window\_not\_found};
        \While{(status = {\it window\_not\_found})}
          \State status = WINDOW(key, pRef, nRef, index);
          \If{(status = {\it window\_not\_found})}
            \State pRef = nRef;
            \State status2 = CLEAN(pRef,nRef);
            \If{(status2 = {\it start\_invalid})}
              \State status = {\it window\_not\_found}
            \EndIf
          \EndIf
        \EndWhile
        \If{(status = {\it window\_found})}
          \State
          \Return status;
        \EndIf
        \If{(status = {\it key\_found})}
          \State
          \Return status;
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\section{Proof of Correctness}

\begin{algorithm}
  \caption{Insert a key in the set}
  \label{alg:insert}
  \begin{algorithmic}[1]
    \Require
       \Statex {\it key} to be searched.
    \Ensure
       \Statex Returns {\it false} if key is found else inserts the {\it key}.

    \Statex
    \Function{insert}{key}
      \State doneFlag := false;
      \While{(!doneFlag)}
        \State findStatus := find(key, prevRef);
        \If{(findStaus = true)}
          \State
          \Return false;
        \EndIf
        \State [nextRef, prevMark] = getUnmarkedRef(prevRef);
        \If{(prevMark = 0)}
          \State insertStatus = false;
          \State minIndex := getMinEmptySlot(nextRef,nodePool);
          \If{(minIndex = 0)} \Comment No empty slot.
            \State insertStatus := insertNodeAndKey(key, prevRef,nextRef);
          \ElsIf{(minIndex > 0)}
            \State insertStatus := insertKey(key, minIndex, prevRef, nextRef);
          \EndIf
          \If{insertStatus = true}
            \State
            \Return true;
          \EndIf
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Find empty slot with minimum index}
  \label{alg:minindex}
  \begin{algorithmic}[1]
    \Require
      \Statex {\it nextRef} in which minumum index to empty slot is to be
              found.
    \Ensure
      \Statex Returns {\it -1} if {\it nextRef} is deleted, {\it 0} if no
              empty slot is found, or minimum index to empty slot.

    \Function{getMinEmptySlot}{nextRef}
      \State val := nextRef:V[lid];
      \State indicator := (val = EMPTY\_SLOT)?lid:0;
      \If {(simdALL(indicator = 0))}
        \State minIndex := 0;
      \Else
        \State minIndex := simdMIN(indicator);
      \EndIf
      \State [nnRef,nextMark] := getUnmarkedPtr(nextRef);
      \If{(nextMark = 0)}
        \State
        \Return minIndex;
      \Else
        \State
        \Return -1;
      \EndIf  
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Insert a node and a key}
  \label{alg:insnodekey}
  \begin{algorithmic}[1]
    \Require
      \Statex {\it key} to be inserted.
      \Statex {\it prefRef} and {\it nextRef} give window in which new node
              and key are to be inserted.
    \Ensure
       \Statex Returns {\it true} if successful.

    \Function{insertNodeAndKey}{key, prevRef, nextRef}
      \If{(lid = 1)} 
        \State newNRef := newNode();
        \State newNNRef := newNode();
      \EndIf
      \State simdBARRIER();
      \State newNRef  := simdBROADCAST(newNRef,1);
      \State newNNRef := simdBROADCAST(newNRef,1);

      \State newNRef:next := [newNNRef,0];
      \If{(nodePool[nextRef]:V[lid] < key)}
        \State nodePool[newNRef]:V[lid] := nodePool[nextRef]:V[lid];
        \State nodePool[newNNRef]:V[lid] := EMPTY\_SLOT;
      \Else
        \State nodePool[newNNRef]:V[lid] := nodePool[nextRef]:V[lid];
        \State nodePool[newNPRef]:V[lid] := EMPTY\_SLOT;
      \EndIf
      \State minIndex := getMinEmptySlot(newNRef,nodePool);
      \State nodePool[newNRef]:V[minIndex] := key;
      \State nodePool[newNNPtr]:next := [nextRef,0];
      \State status := CAS(nodePool[prevRef]:next,[nextRef,0],newNPtr);
      \Return status;
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Insert a key in a node}
  \label{alg:inskey}
  \begin{algorithmic}[5]  
    \Function{insertKey}{key, minIndex, nextRef\&, nodePool}
      \If{lid = 1}
        \State status := CAS(nodePool[nextRef]:V[minIndex],EMPTY\_SLOT,key);
      \EndIf
      \State simdWait();
      \State status = simdBroadcast(status, 1);
      \Return status;
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Delete a key from the set}
  \label{alg:delkey}
  \begin{algorithmic}[5]  
    \Function{remove}{key, nodePool}
      \State doneFlag := false;
      \While{(!doneFlag)}
        \State findStatus := find(key, prevRef\&, nextRef\&, nodePool);
        \If{(findStaus = false)}
          \State
          \Return false;
        \EndIf
        \State val   := nodePool[nextRef]:V[lid];
        \If{(val = key)}
          \State status := CAS(nodePool[nextRef]:V[lid],key,EMPTY\_SLOT);
        \EndIf
        \State simdWait();
        \State status := simdBrodacast(status);
        \If{(status = true)}
          \State status := deleteNode(prevRef\&, nextRef\&, nodePool);
          \Return status;
        \Else
          \State
          \Return false;
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{Delete a node}
  \label{alg:delnode}
  \begin{algorithmic}[5]  
    \Function{deleteNode}{prevRef\&, nextRef\&, nodePool}
         \State val := nodePool[nextRef]:V[lid];
         \State status := simdAll(val,EMPTY\_SLOT);
         \If{(status = true)}
           \State [nnRef,nextMark] := getPtr(nextRef);
           \State newMark := 1;
           \If{(lid = 1)}
              \State status := CAS(nodePool[nextRef]:next,[nnRef,nextMark],[nnRef,newMark]);
              \If{(status = true)}
                \State status = delMarkedNodes(prevRef,NodePool); 
              \EndIf
           \EndIf
           \State simdWait();
           \State status = simdBroadcast(status,1);
           \State
           \Return status;
         \EndIf
    \EndFunction
  \end{algorithmic}
\end{algorithm}

>>>>

\begin{algorithm}
  \caption{finds a key and returns a window to it.}
  \label{alg:find}
  \begin{algorithmic}[1]
    %\Require
    %    \Statex startRef:Reference to the starting node.
    %\Ensure
    %   \Statex cleans all the logically deleted nodes.
    \Statex   
    \Function{find}{key, prevRef\&, nextRef\&, index\&}
      \State startRef = hash(key);
      \State prevRef = nextRef = {\it Null};
      \State index = 0;      
      \While{(true)}
        \State pRef = {\it Null};
        \State nRef = startRef;
        \State status = {\it window\_not\_found};
        \While{(status = {\it window\_not\_found})}
          \State status = WINDOW(key, pRef, nRef, index);
          \If{(status = {\it window\_not\_found})}
            \State pRef = nRef;
            \State status2 = CLEAN(pRef,nRef);
            \If{(status2 = {\it start\_invalid})}
              \State status = {\it window\_not\_found}
            \EndIf
          \EndIf
        \EndWhile
        \If{(status = {\it window\_found})}
          \State
          \Return status;
        \EndIf
        \If{(status = {\it key\_found})}
          \State
          \Return status;
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{clones a node and adds a key to it.}
  \label{alg:clone}
  \begin{algorithmic}[1]
    %\Require
    %    \Statex startRef:Reference to the starting node.
    %\Ensure
    %   \Statex cleans all the logically deleted nodes.
    \Statex   
    \Function{clone}{ref, key}
      \State newRef = ALLOC();
      \Comment{assumption is that ALLOC always returns a node}
      \State newRef:next = ref:next;
      \State keyIndex = simdIndex(ref:val = key);
      \If{keyIndex = 0}
        \State minIndex    = min(simdIndex(ref:val = {\it empty}));
        \Comment{simdIndex returns zero if condition is not met}         
        \If{(minIndex $\not =$ 0)}
          \State simdCopy(ref:val, newRef:val);
          \State newRef:val[minIndex] = key;
          \State
          \Return newRef;
        \Else
          \State prevNewRef = ALLOC();
          \State simdCopy(ref:val, prevNewRef:val, (ref:val < key));
          \State simdCopy(ref:val, newRef:val, (ref:val > key));
          \State prevNewRef:next = [newRef,[0,0,0]];
          \State minIndex    = min(simdIndex(newRef:val = {\it empty}));      
          \State newRef:val[minIndex] = key;
          \State
          \Return prevNewRef;
        \EndIf
      \Else
        \State simdCopy(ref:val, newRef:val);
        \State newRef:val[keyIndex] = {\it empty};
        \State
        \Return newRef;
      \EndIf  
      \State
      \Return {\it null};
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{traverses the list from prev ref to next ref.}
  \label{alg:traverse}
  \begin{algorithmic}[1]
    %\Require
    %    \Statex startRef:Reference to the starting node.
    %\Ensure
    %   \Statex cleans all the logically deleted nodes.
    \Statex   
    \Function{traverse}{prevRef, nextRef}
      \State pRef = prevRef;
      \State [nRef, pBits] = unpackRef(pRef:next);
      \While{(pBits = [0,x,x])}
        \If{(nRef $\not = $ nextRef)}
          \State pRef = nRef;
          \State [nRef, pBits] = unpackRef(pRef:next);
        \Else
          \State
          \Return pRef;
        \EndIf
      \EndWhile
      \State
      \Return {\it null};
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{adds a key to the set.}
  \label{alg:add}
  \begin{algorithmic}[1]
    %\Require
    %    \Statex startRef:Reference to the starting node.
    %\Ensure
    %   \Statex cleans all the logically deleted nodes.
    \Statex   
    \Function{add}{key}
      \While{(true)}
        \State status = FIND(key, prevRef nextRef,index);
        \If{status = {\it window\_found}}
          \State pRef = TRAVERSE(prevRef, nextRef);
          \If{(pRef $\not =$ {\it null})}
            \State cloneRef = CLONE(nextRef,key);
            \State status = REPLACE(pRef,cloneRef);
            \If{(status = {\it replaced})}
              \State
              \Return {\it true};
            \EndIf
          \EndIf
        \Else
          \State
          \Return {\it false}
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

\begin{algorithm}
  \caption{removes a key from the set.}
  \label{alg:remove}
  \begin{algorithmic}[1]
    %\Require
    %    \Statex startRef:Reference to the starting node.
    %\Ensure
    %   \Statex cleans all the logically deleted nodes.
    \Statex   
    \Function{remove}{key}
      \While{(true)}
        \State status = FIND(key, prevRef nextRef,index);
        \If{status = {\it key\_found}}
          \State pRef = TRAVERSE(prevRef, nextRef);
          \If{(pRef $\not =$ {\it null})}
            \State cloneRef = CLONE(nextRef,key);
            \State status = REPLACE(pRef,cloneRef);
            \If{(status = {\it replaced})}
              \State
              \Return {\it true};
            \EndIf
          \EndIf
        \Else
          \State
          \Return {\it false}
        \EndIf
      \EndWhile
    \EndFunction
  \end{algorithmic}
\end{algorithm}

%\section{Proof of Correctness}
